additional3D

### 2021-05-25 additional.Rmd
ok plotly

lowE <- plot_ly(df_sqbl)  %>%
  add_trace(x=df_sqbl$fraction_blue,y=df_sqbl$circle_orange,z=df_sqbl$de_sq_bl,
            scene = "scene1",
                                        name = "Ethnic",
                                       type="scatter3d",
                                       mode="markers",
                                     marker = list(cmin=0,cmax=1,
                                                   # colorscale = "Reds",
                                     colorscale =  list(
                                        c(0,'pink'),
                                        c(0.25,'red'),
                                        c(0.5,'green'),
                                        c(0.75,'blue'),
                                        c(1, 'purple')),
                                       color= df_sqbl$et_sq_bl, showscale = T)

            )  %>% 
  layout(showlegend = F,
         title="Ethnic",
         scene = list(
      xaxis = list(title = "Ethnic Ratio",range=seq(50,90,by=10),dtick=10),
      yaxis = list(title = "% Liberal Minority",autorange = "reversed"),
      zaxis = list(title = "Cluster")))

 lowV<- plot_ly(df_sqbl)  %>%   add_trace(x=df_sqbl$fraction_blue,y=df_sqbl$circle_orange,z=df_sqbl$dv_sq_bl,
                                          scene =  "scene2",
                                     name = "Value",
                                     type="scatter3d",
                                     mode="markers",
                                    marker = list(cmin=0,cmax=1,
                                                   # colorscale = "Reds",
                                     colorscale =  list(
                                        c(0,'pink'),
                                        c(0.25,'red'),
                                        c(0.5,'green'),
                                        c(0.75,'blue'),
                                        c(1, 'purple')),
                                       color= df_sqbl$et_sq_bl, showscale = T)

            )  %>% 
       layout(showlegend = T,
         title="",
         scene = list(
      xaxis = list(title = "Ethnic Ratio",range=seq(50,90,by=10),dtick=10),
      yaxis = list(title = "% Liberal Minority",autorange = "reversed"),
      zaxis = list(title = "Cluster")))

A <- subplot(lowE,lowV) %>% layout(annotations = list(
 list(x = 0.2 , y = 1 , text = "Ethnic", showarrow = F, xref='paper', yref='paper'),
  list(x = 0.8 , y = 1, text = "Value", showarrow = F, xref='paper', yref='paper'))
)

>>>>

lowE <- plot_ly(df_sqbl)  %>%
  add_trace(x=df_sqbl$fraction_blue,y=df_sqbl$circle_orange,z=df_sqbl$de_sq_bl,
            scene = "scene1",
                                       # name = "Ethnic",
                                       type="scatter3d",
                                       mode="markers",
                                     marker = list(
                                       #cmin=0,cmax=1,
                                           colorscale = "Reds",
                                     # colorscale =  list(
                                     #    c(0,'pink'),
                                     #    c(0.25,'red'),
                                     #    c(0.5,'green'),
                                     #    c(0.75,'blue'),
                                     #    c(1, 'purple')),
                                       color= df_sqbl$et_sq_bl, showscale =  T,
                                     colorbar=list(title = "Ethnic \nExposure" ,y = 0.3, len = 0.5, yanchor='top'))

            )  %>% 
  layout(showlegend = F,
         #title="Ethnic",
         "scene1" = list(
      xaxis = list(title = "Ethnic Ratio",range=seq(50,90,by=10),dtick=10),
      yaxis = list(title = "% Liberal Minority",autorange = "reversed"),
      zaxis = list(title = "Ethnic Cluster")))

 lowV<- plot_ly(df_sqbl)  %>%   add_trace(x=df_sqbl$fraction_blue,y=df_sqbl$circle_orange,z=df_sqbl$dv_sq_bl,
                                          scene =  "scene2",
                                   #  name = "Value",
                                     type="scatter3d",
                                     mode="markers", 
                                     marker = list( #cmin=0,cmax=1,
                                                   # colorscale = "Reds",
                                     colorscale = "Blues",
                                       # list(
                                       #  c(0,'pink'),
                                       #  c(0.25,'red'),
                                       #  c(0.5,'green'),
                                       #  c(0.75,'blue'),
                                       #  c(1, 'purple'))

                                    color= df_sqbl$et_sq_bl , showscale = T, reversescale=T,
                                     colorbar=list(title = "Value  \nExposure", y = 0.3, len=0.5, yanchor='bottom'))
            )  %>% 
       layout(showlegend = F,
         "scene2" = list(
      xaxis = list(title = "Ethnic Ratio",range=seq(50,90,by=10),dtick=10),
      yaxis = list(title = "% Liberal Minority",autorange = "reversed"),
      zaxis = list(title = "Value Cluster")))

axx <- list(
  title = "Ethnic Ratio"
)

axy <- list(
  title = "% Liberal Minority"
)

axz <- list(
  title = "Ethnic Cluster"
)

A <- subplot(lowE, lowV)  %>%

  layout(title =  "Conservative Locals"
)

b <- subplot(
  add_markers(plot_ly(x=df_sqbl$fraction_blue,y=df_sqbl$circle_orange,z=df_sqbl$de_sq_bl),color=df_sqbl$et_sq_bl) %>% colorbar(title= "Ethnic")

)

c <- subplot(
  add_markers(plot_ly(x=df_sqbl$fraction_blue,y=df_sqbl$circle_orange,z=df_sqbl$dv_sq_bl),color=df_sqbl$vl_sq_bl) %>% colorbar(title = "Value")

)

A <- subplot(b,c)
